%
% PROJECT: <ETD> Electronic Thesis and Dissertation Initiative
%   TITLE: LaTeX report template for ETDs in LaTeX
%  AUTHOR: Neill Kipp, nkipp@vt.edu
%     URL: http://etd.vt.edu/latex/
% SAVE AS: etd.tex
% REVISED: September 6, 1997 [GMc 8/30/10]
% 

% Instructions: Remove the data from this document and replace it with your own,
% keeping the style and formatting information intact.  More instructions
% appear on the Web site listed above.

\documentclass[12pt]{report}
% \documentclass[12pt,dvips]{report} %% TODO CHANGED THIS .. removed dvips .. printer friendly


\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.5in}
\setlength{\evensidemargin}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\topmargin}{0in}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.1in}

%\setcounter{secnumdepth}{3}
%\setcounter{tocdepth}{3}

% Uncomment for double-spaced document.
\renewcommand{\baselinestretch}{1.3}
\newcommand{\des}{\textit{Discrete Event Simulator}}
\usepackage{graphicx}
\graphicspath{ {images/} }
%\graphicspath{ {/root/thesis/images/} }
\usepackage{url, listings, color}
\usepackage{etoolbox}
\usepackage [ruled,vlined,algo2e]{algorithm2e}
\newbool{toShowBibliography} % var to show bibliography


\usepackage{titlesec}
\usepackage{hyperref}

\titleclass{\subsubsubsection}{straight}[\subsection]

\newcounter{subsubsubsection}
\renewcommand\thesubsubsubsection{\thesubsubsection.\arabic{subsubsubsection}}
\renewcommand\theparagraph{\thesubsubsubsection.\arabic{paragraph}} % optional; useful if paragraphs are to be numbered

\titleformat{\subsubsubsection}
  {\normalfont\normalsize\bfseries}{\thesubsubsubsection}{1em}{}
\titlespacing*{\subsubsubsection}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{5}{\z@}%
  {3.25ex \@plus1ex \@minus.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries}}
\renewcommand\subparagraph{\@startsection{subparagraph}{6}{\parindent}%
  {3.25ex \@plus1ex \@minus .2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries}}
\def\toclevel@subsubsubsection{4}
\def\toclevel@paragraph{5}
\def\toclevel@paragraph{6}
\def\l@subsubsubsection{\@dottedtocline{4}{7em}{4em}}
\def\l@paragraph{\@dottedtocline{5}{10em}{5em}}
\def\l@subparagraph{\@dottedtocline{6}{14em}{6em}}
\makeatother
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}


\begin{document}

\thispagestyle{empty}
\pagenumbering{roman}
\begin{center}

% TITLE
{\Large 
Device Driver isolation using virtual machines
}

\vfill

Sushrut Shirole

\vfill

Thesis submitted to the Faculty of the \\
Virginia Polytechnic Institute and State University \\
in partial fulfillment of the requirements for the degree of

\vfill

Master of Science \\
in \\
Computer Science \& Applications

\vfill

Dr. Godmar Back, Chair \\
Dr. Keith Bisset \\
Dr. Kirk Cameron\\


\vfill

Dec 12, 2013 \\
Blacksburg, Virginia

\vfill

Keywords: Device driver, Virtual machines, domain,  
\\
Copyright 2013, Sushrut Shirole

\end{center}

\pagebreak

\thispagestyle{empty}
\begin{center}

{\large 
Device driver isolation using virtual machines.
}

\vfill

Sushrut Shirole

\vfill

(ABSTRACT)
\end{center}

In majority of today's operating system architectures, kernel is tightly coupled with the device drivers. In such cases, failure in critical components can lead to system failure.
A malicious or faulty device driver can make the system unstable, thereby reducing the robustness. Unlike user processes, a simple restart of the device driver is not possible. In such circumstances a complete system reboot is necessary for complete recovery. In a virtualized environment or infrastructure where multiple operating systems execute over a common hardware platform, cannot afford to reboot the entire hardware due to a malfunctioning of a third party device driver. 
 
The solution we implement exploits the virtualization to isolate the device drivers from the kernel. In this implementation, a device driver serves the user process by running in a separate virtual machine and hence is isolated from kernel. This proposed solution increases the robustness of the system, benefiting all critical systems.
 
To support the proposed solution, we implemented a prototype based on linux kernel and Xen hypervisor. In this prototype we create an independent device driver domain for Block device driver. Our prototype demonstrate that a block device driver can be run in a separate domain. 
 
We isolate device drivers from the kernel with two different approaches and compare both the results. In first approach, we implement the device driver isolation using an interrupt-based inter-domain signaling facility provided by xen hypervisor called event channels. In second approach, we implement the solution, using spinning threads. In second approach user application puts the request in request queue asynchronously and independent driver domain spins over the request queue to check if a new request is available. Event channel is an interrupt-based inter-domain mechanism and it involves immediate context switch, however, spinning doesn't involve immediate context switch and hence can give different results than event channel mechanism. 


\vfill

% GRANT INFORMATION

\pagebreak

% Dedication and Acknowledgments are both optional
% \chapter*{Dedication}

\chapter*{Acknowledgments}
\input{chapters/Acknowledgments.tex}

\tableofcontents
\pagebreak

\listoffigures
\pagebreak

\listoftables
\pagebreak

\pagenumbering{arabic}
\pagestyle{myheadings}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Introduction} 
\markright{Sushrut Shirole \hfill Chapter 1. Introduction \hfill}

\input{chapters/introduction.tex}

\chapter{Background}  
\markright{Sushrut Shirole \hfill Chapter 2. Background \hfill}

\input{chapters/Background.tex}

% System Overview/Architecture
\chapter{System Introduction}
\markright{Sushrut Shirole \hfill Chapter 3. System Introduction \hfill}

\input{chapters/systemintroduction.tex}

\chapter{System Design and Implementation}
\markright{Sushrut Shirole \hfill Chapter 4. System Design and Implementation \hfill}

\input{chapters/implementation.tex}

\chapter{Related Work}
\markright{Sushrut Shirole \hfill Chapter 5. Related Work \hfill}

\input{chapters/relatedwork.tex}


\chapter{Evaluation}
\markright{Sushrut Shirole \hfill Chapter 6. Evaluation \hfill}

\input{chapters/Evaluation.tex}

\chapter{Conclusion and Future Work}
\markright{Sushrut Shirole \hfill Chapter 7. Conclusion and Future Work \hfill}

\input{chapters/conclusion.tex}


%%%%%%%%%%%%%%%%
% Do tables like this:

%  \begin{table}
%  \caption{The Graduate School wants captions above the tables.}
% \begin{center}
%  \begin{tabular}{ccc}
%  x & 1 & 2 \\ \hline
%  1 & 1 & 2 \\
%  2 & 2 & 4 \\ \hline
%  \end{tabular}
% \end{center}
%  \end{table}

%%%%%%%%%%%%%%%%%
% all sections and sub-sections

%\part
%\chapter (report style only)
%\section
%\subsection
%\subsubsection
%\paragraph
%\subparagraph
%\subsubparagraph (milstd and book-form styles only)
%\subsubsubparagraph (milstd and book-form styles only)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\chapter*{Bibliography}
\nocite{*}
\bibliographystyle{plain}
\bibliography{references}

% \appendix

% In LaTeX, each appendix is a "chapter"
% \chapter{Program Source}

\end{document}


%
%


